Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

    \item Conversely, consider that $\J(R_1, R_2, R_3)$ is non-empty. Consider an arbitrary result tuple $(r_1, r_2, r_3) \in \J(R_1, R_2, R_3)$. Assume, w.l.o.g., that $r_1 = (-\infty, \infty) \times [u, u] \times [v, v]$.
    Because the z-projection of $r_2$ must match that of $r_1$, we assert that $r_2$ must have the form $[w, w] \times (-\infty, \infty) \times [v, v]$ for some $w > u$. Because the x-projection of $r_3$ must match that of $r_2$ and the y-projection of $r_3$ must match that of $r_1$, it follows that $r_3$ must have the form $[w, w] \times [u, u] \times (-\infty, \infty)$. This means that the edges $\set{u,v}$, $\set{v,w}$, and $\set{u,w}$ must all exist in $G$, and thus form a triangle.
}

>>>>

    \item Conversely, consider that $\J(R_1, R_2, R_3)$ is non-empty. Consider an arbitrary result tuple $(r_1, r_2, r_3) \in \J(R_1, R_2, R_3)$. Assume, w.l.o.g., that $r_1 = (-\infty, \infty) \times [u, u] \times [v, v]$, where $u < v$.
    Because the z-projection of $r_2$ must match that of $r_1$, we assert that $r_2$ must have the form $[w, w] \times (-\infty, \infty) \times [v, v]$ for some $w > v$. Because the x-projection of $r_3$ must match that of $r_2$ and the y-projection of $r_3$ must match that of $r_1$, it follows that $r_3$ must have the form $[w, w] \times [u, u] \times (-\infty, \infty)$. This means that the edges $\set{u,v}$, $\set{v,w}$, and $\set{u,w}$ must all exist in $G$, and thus form a triangle.
}
